\section{Introduction}
\label{Sect:Intro}

\textbf{Author: Chris Rogers}

\emph{Strategy - the aim of the paper is to show that MICE reduces normalised 
emittance and this is consistent with MC. In order to demonstrate this, we 
select 2016/04 1.2 and 2016/04 1.5 as the cooling channel settings to use (they 
are likely to have best cooling and 1.5 also supports Ao's IPAC paper). The
analysis is intended to be a `minimal' analysis, i.e. we get just enough to
prove emittance reduction. We don't have to do all the fancy analyses yet, but 
we do have to be correct and rigorous.}

\subsection{Ionisation Cooling}
Description of ionisation cooling and usual blah blah.

\subsection{The Muon Ionisation Cooling Experiment}
Description of the equipment (hardware perspective) i.e. detectors, magnets, etc.

\subsection{Data Taken in 2016/04}
During 2016/04, data was recorded for several settings.The cooling channel 
magnet set currents and the beam optical parameters assuming the paraxial 
approximation are listed in table \ref{tab:magnet_parameters}. This note 
concerns analysis of two cooling channel settings `2016-04 1.2' and
`2016-04 1.5'.

Beam data was taken with the two settings with beam momentum 140 MeV/c and three
emittance settings. Additionally, data was taken with 170, 200 and 240 MeV/c
data in order to measure the magnetic alignment of the cooling channel.

\begin{table}
\centering
\caption{Magnet parameters for 2016/04. Trim power supplies on SSU and SSD were
not operational. Focus coils were powered in solenoid mode. Match coils on SSD
were not powered.
\label{tab:magnet_parameters}}

\begin{tabular}{|l|ccccc|}

\hline
Setting                       & 2016/04 1.3 & 2016/04 1.2 & 2016/04 1.5 & 2016/04 2.3 & 2016/04 2.4 \\
\hline
Start time                    & 18/11 20:00 & 28/11 16:50 & 05/12 13:20 & 08/12 16:30 & 12/12 14:20 \\
End time                      & 23/11 14:10 & 05/12 11:00 & 08/12 14:10 & 12/12 11:20 & 14/12 03:20 \\
Nominal FC $\beta_\perp$ [mm] & & & & & \\
Nominal momentum [MeV/c]      & 140         & 140         & 140         & 200         & 240         \\
\hline
SSU Center Coil [A]           & 205.5       & 205.86      & 208.0       & 208.0       & 208.0       \\
SSU Match Coil2 [A]           & 208.6       & 171.9       & 187.4       & 172.9       & 193.1       \\
SSU Match Coil1 [A]           & 102.3       & 211.7       & 178.1       & 239.2       & 177.7       \\
\hline
FC Coil [A]                   & 41.5        & 57.9        & 55.2        & 56.2        & 78.8       \\
\hline
SSD Center Coil [A]           & 205.5       & 205.86      & 208.0       & 208.0       & 208.0       \\
\hline
\end{tabular} 

\end{table}


